\phantomsection
\addcontentsline{toc}{chapter}{\bf ACKNOWLEDGEMENTS}
\begin{center}
    \large{\bf ACKNOWLEDGEMENTS}
\end{center}

I would like to express my sincere gratitude to my advisor Prof. Chaklam Shilpasuwanchai for his continuous support, motivation and guidance since the very beginning of my research. His insightful advice on research and writing has provided me with a direction to follow. I could not have asked for a better advisor for my thesis study.

I am also extremely grateful to Akraradet Sinsamerusk (Jo), my supervisor, who deserves immense recognition for his unparalleled contribution. Without his exceptional assistance, this accomplishment would not have been possible. Jo consistently offered solutions to the challenges I encountered, and his remarkable genius continues to inspire me. His relentless hard work has served as a constant source of inspiration, and I consider myself fortunate to have had such a knowledgeable and supportive supervisor.

Besides my sincere thanks also goes to the rest of my thesis committee: Prof. Matthew N. Dailey, Dr. Mongkol Ekpanyapong for accepting to be on my examination committee. I am grateful for their time, guidance, and contributions to my research.

I would also like to express my sincere gratitude to the entire AIT Brain Lab team. Working alongside such positive and energetic individuals made this journey truly memorable and fun. Within the lab, I want to extend a special thanks to Fathima and Pongkorn for their invaluable assistance in helping me get started with EEG. Also I cannot forget my friends in AIT who were always there to lend a listening ear and and provide support when I needed the most.

Last but not the least, I want to thank my family for their unwavering emotional support and constant words of encouragement. My heartfelt thanks go to my mother, father, brother, and sister-in-law, who have always been there for me. They have continuously reminded me of my capabilities and have been my pillars of strength during the lowest points of this journey. My mother, in particular, deserves special recognition for her unwavering belief in my abilities and unwavering motivation. It would not have been possible with her.


